Title

### 2025-02-04 index.qmd
working towards a more perfect union

```{r, echo=FALSE, results='asis'}
insert_figure <- function(rq, metro, graph_type, base_path = graphs_dir) {
  metro <- str_replace_all(string = metro, pattern = ' ', replacement = '_')

  fig_file <- file.path(base_path, str_c(rq, '_', metro, '_', graph_type, '.png'))
  cap_file <- file.path(base_path, str_c(rq, '_', metro, '_', graph_type, '_title.txt'))
  note_file <- file.path(base_path, str_c(rq, '_', metro, '_', graph_type, '_note.txt'))

  # Print caption
  writeLines(paste0('#### ', readLines(cap_file, warn = F)))

  # Output the figure block to the doc
  writeLines(paste0('![](', fig_file, ')\n'))

  # Print footnotes
  writeLines(paste0('<div class="footnote">', paste0(readLines(note_file, warn = F), collapse = '</br>'), '</div>'))
}

@@

  # Print a top-level heading for the metro area
  writeLines(paste0('## ', toTitleCase(m), ' area'))

  for (rq in rqs) {
    rq_num <- str_replace(string = rq, pattern = 'rq', replacement = '')

    if (rq == 'rq1') { # rq1 run for every metro area

      for (g in graph_types) {

        # Print a heading for the RQ
        writeLines(paste0('### Research question ', rq_num))

@@

    } else if (rq == 'rq2' & (m %in% c('chicago','philadelphia'))) { # rq2 run only for specific metro areas and orders

      # Separate rq2 graphs for race and for firstgen status; they apply to all above metro areas
      for (suffix in c('race_row_plot', 'race_col_plot', 'firstgen_row_plot', 'firstgen_col_plot')) {

        # Print a heading for the RQ
        writeLines(paste0('### Research question ', rq_num))

        insert_figure(metro = m, rq = rq, graph_type = suffix)

      }

      if (m == 'chicago') {

        # Print a heading for the RQ
        writeLines(paste0('### Research question ', rq_num))

        insert_figure(metro = m, rq = rq, graph_type = 'order_487984_race_by_firstgen')

        # Print a heading for the RQ
        writeLines(paste0('### Research question ', rq_num))

        insert_figure(metro = m, rq = rq, graph_type = 'order_488035_488053_race_by_firstgen')

      } else if (m == 'philadelphia') {

        # Print a heading for the RQ
        writeLines(paste0('### Research question ', rq_num))

        insert_figure(metro = m, rq = rq, graph_type = 'order_448922_race_by_firstgen')

        # Print a heading for the RQ
        writeLines(paste0('### Research question ', rq_num))

        insert_figure(metro = m, rq = rq, graph_type = 'order_448427_448440_race_by_firstgen')

      }
    }
  }
}
```

>>>>

```{r, echo=FALSE, results='asis'}
insert_figure <- function(rq, metro, graph_type, base_path = graphs_dir) {
  # Convert spaces -> underscores for filenames
  metro <- str_replace_all(string = metro, pattern = " ", replacement = "_")

  fig_file  <- file.path(base_path, str_c(rq, "_", metro, "_", graph_type, ".png"))
  cap_file  <- file.path(base_path, str_c(rq, "_", metro, "_", graph_type, "_title.txt"))
  note_file <- file.path(base_path, str_c(rq, "_", metro, "_", graph_type, "_note.txt"))

  # Print caption
  writeLines(paste0("#### ", readLines(cap_file, warn = FALSE)))

  # Output the figure block to the doc
  writeLines(str_c("![](", fig_file, ")\n"))

  # Print footnotes
  writeLines(
    str_c("<div class=\"footnote\">",
          paste0(readLines(note_file, warn = FALSE), collapse = "</br>"),
          "</div>")
  )
}

@@

  # Print a top-level heading for the metro area
  writeLines(str_c("## ", toTitleCase(m), " area"))

  for (rq in rqs) {
    rq_num <- str_replace(string = rq, pattern = "rq", replacement = "")

    if (rq == "rq1") { 
      # ---------------------------------------
      #  rq1 => run for every metro area 
      # ---------------------------------------
      for (g in graph_types) {
        # Print a heading for the RQ
        writeLines(str_c("### Research question ", rq_num))

@@

    } else if (rq == "rq2" & (m %in% c("chicago","philadelphia","los angeles","orange county","san diego","bay area"))) {
      # -------------------------------------------------
      # rq2 => run only for the specified metro areas
      # -------------------------------------------------

      # 1) For LA & Bay Area, we have SEPARATE row/col plots per order (2 files each).
      # 2) For all other metros in this subset, we still do the old "combined" row/col plots.

      # If LA or Bay Area => do the "separate" approach
      if (m %in% c("los angeles","bay area")) {

        # We'll insert each of the 8 new plots: race_row_plot_..., race_col_plot_...,
        # and firstgen_row_plot_..., firstgen_col_plot_...
        # Each suffix also ends with the order ID.
        for (suffix in c(
          "race_row_plot_448375", "race_row_plot_448374_448420",
          "race_col_plot_448375", "race_col_plot_448374_448420",
          "firstgen_row_plot_448375", "firstgen_row_plot_448374_448420",
          "firstgen_col_plot_448375", "firstgen_col_plot_448374_448420"
        )) {
          writeLines(str_c("### Research question ", rq_num))
          insert_figure(metro = m, rq = rq, graph_type = suffix)
        }

      } else {
        # For the other metros in the same set
        # (chicago, philadelphia, orange county, san diego):
        # we still show the combined row/col figure:

        for (suffix in c("race_row_plot", "race_col_plot",
                         "firstgen_row_plot", "firstgen_col_plot")) {
          writeLines(str_c("### Research question ", rq_num))
          insert_figure(metro = m, rq = rq, graph_type = suffix)
        }
      }

      # -------------------------------------------------
      # Then your custom calls by city:
      # -------------------------------------------------
      if (m == "chicago") {
        # two separate calls for 'chicago' order IDs
        writeLines(str_c("### Research question ", rq_num))
        insert_figure(metro = m, rq = rq, graph_type = "order_487984_race_by_firstgen")

        writeLines(str_c("### Research question ", rq_num))
        insert_figure(metro = m, rq = rq, graph_type = "order_488035_488053_race_by_firstgen")

      } else if (m == "philadelphia") {
        # likewise for 'philadelphia'
        writeLines(str_c("### Research question ", rq_num))
        insert_figure(metro = m, rq = rq, graph_type = "order_448922_race_by_firstgen")

        writeLines(str_c("### Research question ", rq_num))
        insert_figure(metro = m, rq = rq, graph_type = "order_448427_448440_race_by_firstgen")

      } else if (m %in% c("los angeles","orange county","san diego","bay area")) {
        # likewise for these 4 metros
        writeLines(str_c("### Research question ", rq_num))
        insert_figure(metro = m, rq = rq, graph_type = "order_448375_race_by_firstgen")

        writeLines(str_c("### Research question ", rq_num))
        insert_figure(metro = m, rq = rq, graph_type = "order_448374_448420_race_by_firstgen")
      }

    } # end of rq==rq2 section

  } # end of rqs

} # end of metros

```
